%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
% Modified by Deanna M. Church
% Last updated: Mar 10, 2018
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{dmc-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{DeannaM}{Church}{Genomics, Technology and Bioinformatics Leader} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
    \section{contact}
    3538 22nd St.
    Boulder, CO 80304
    USA
    {\Large\textcolor{gray}{\Mobilefone}} \hfill (301) 233-2991
    \href{mailto:deanna.church@gmail.com}{deanna.church@gmail.com}
    ~
    \tlogo \hfill \href{http://twitter.com/deannachurch}{@deannachurch}
    \llogo \hfill \href{https://www.linkedin.com/in/deanna-church-a8749513/}{in://deannachurch}
    \ghlogo \hfill \href{https://www.github.com/deannachurch}{gh://deannachurch}
    ~
    \section{leadership skills}
    Empathy, Communication, 
    Mentorship, Team Player,
    Curiosity, Initiative \&
    Strategic and 
    Critical Thinking
    
    \section{product skills}
    Product definition,
    Product commercialization, 
    Product management,
    Applications,  
    Writing \& Presentations
    
    \section{genomics}
    Genome assembly,
    Genome annotation,
    Variant analysis,
    Functional genomics \& 
    Genome editing
    
    \section{bioinformatics}
    Python, Data Science, R, 
    Git, HTML, XML/XSLT, 
    Javascript, CSS3 \& SQL
    
    \end{aside}

%----------------------------------------------------------------------------------------
% FOCUS SECTION
%----------------------------------------------------------------------------------------
\section{focus}
Leading interdisciplinary teams that match new technology to research needs. A systems level thinker comfortable diving deep into the data and delivering 
high level strategic plans. 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
    %------------------------------------------------
    \entry
    {2023 - Present}
    {General Inception}
    {Remote}
    {\emph{Executive-in-Residence}\\
    Driving diligence, operational excellence and providing executive leadership for General Inception companies. }
    
    \entry
    {2022 - Present}
    {dmchurch bio, llc}
    {Boulder, CO}
    {\emph{Principal}\\
    Independent consultant with a focus on genomics, funcational genomes and data analysis. 
    }
    
    \entry
    {2021--2022}
    {Inscripta, Inc}
    {Boulder, CO}
    {\emph{Vice President, Mammalian Business Area and Software Strategy}\\
    Reported to the CEO. Established requirements and drove software changes required to scale from 10s of genomes to 1000s of 
    genomes (80\% of customer base).  Led a functional genomics team to establish single cell measurements to accelerate product development.
    Led a Data Science team developing new analysis methods critical for customer success. 
    }
    
    \entry
    {2019--2021}
    {Inscripta, Inc}
    {Boulder, CO}
    {\emph{Senior Director, Applications Mammalian}\\
    Reported to the CEO. Established customer requirements for the mammalian platform to enter a multimillion dollar market. 
    Communicated requirements to a multidisciplinary product team. Contributed to three patents critical for application success.
    }
    
    \entry
    {2016--2018}
    {10x Genomics}
    {Pleasant, CA}
    {\emph{Senior Director of Applications} \\
    Led a team of scientists demonstrating the value of the 10x platforms, 
    contributing to 14 published manuscripts and a dozen Application notes across the product portfolio. 
    Presented at over 40 conferences and meetings, leading to wide spread adoption of 10x products. 
    }
    
    \entry
    {2014-2016}
    {Personalis, Inc}
    {Menlo Park, CA}
    {\emph{Senior Director of Genomics and Content} \\
    Led a team developing novel genome analysis algorithms, pipelines and knowledge bases built to support genome 
    interpretation, cutting report generation by half. Worked collaboratively with partners and government agencies 
    to establish best practices for genome analysis and interpretation. 
    }
    
    \entry
    {2001-2014}
    {National Center for Biotechnology Information, NIH}
    {Bethesda, MA}
    {\emph{Staff Scientist} \\
    Led large international collaborations and led the development teams for NCBI systems serving 1000s of users daily.
    Contributed to or led the development of over 10 public resources, including the Genome Reference Consortium and Clinvar.
    }
    
    %\entry
    %{1990-1992}
    %{MIT and MGH}
    %{Boston, MA}
    %{\emph{Laboratory Technician}\\
    %Managed laboratory and performed experiments, including helping to develop the exon amplification protocol.
    %}
    \end{entrylist}

%----------------------------------------------------------------------------------------
%	SERVICE AND COMMUNITY PARTICIPATION
%----------------------------------------------------------------------------------------

\section{scholarship and service}
Published over 70 manuscripts and given over 100 scientific presentations, including many keynotes. Serves on scientific advisory boards, currently including Human Pangenome Reference Consortium and Genome Quebec. Reviews scientific manuscripts and grants. \\

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry 
{2024-2025}
{Springboard Data Science Program}
{Boulder, CO}
{
%Hands on data science training.
}

\entry
{1999-2001}
{National Center for Biotechnology Information, NIH}
{Bethesda, MD}
{\emph{Postdoctoral fellow}
%Coordinated mouse genome resources.
}
%------------------------------------------------
\entry
{1997-1999}
{Laboratory of Janet Rossant, Mt. Sinai Hospital}
{Toronto, Ontario}
{\emph{Postdoctoral fellow}
%Applying genomics methods to understanding mouse developmental biology
}
%------------------------------------------------
\entry
{1992-1997}
{PhD {\normalfont of Biological Sciences}}
{The University of California, Irvine}
%{\emph{Phenotype-genotype correlation in the Cri-du-Chat region of chromosome 5}

%------------------------------------------------
\entry
{1986-1990}
{Bachelor {\normalfont of Liberal Arts}}
{University of Virginia}
%{\emph{Research project focused on cell cycle regulation using yeast}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{scholarship}
%{Authored over 50 scientific manuscripts.}
%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books from the bibliography

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
%\end{refsection}

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------
\end{document}
